\begin{thebibliography}{99}

\bibitem{cisco-internet-traffic}
\textit{"Visual Networking Index"}, Cisco Systems, \texttt{http://www.cisco.com/c/en/us/solutions/collateral/service-provider/visual-networking-index-vni/mobile-white-paper-c11-520862.html}
  
\bibitem{http://www.internetlivestats.com/total-number-of-websites/}
\texttt{http://www.internetlivestats.com/total-number-of-websites/}

\bibitem{ShkapenyukSuel} 
Vladislav Shkapenyuk and Torsten Suel.
\textit{Design and Implementation of a High-Performance Distributed Web Crawler}.\\
\texttt{http://cis.poly.edu/tr/tr-cis-2001-03.pdf}

\bibitem{Pantil} 
Yugandhara Patil and Sonal Patil.
\textit{Review of Web Crawlers with Specification and Working}.\\
\texttt{http://www.ijarcce.com/upload/2016/january-16/IJARCCE\%2052.pdf}

\bibitem{GautamPadminiFilippo} 
Pant Gautam, Srinivasan Padmini and Menczer Filippo.
\textit{Crawling the Web}.\\
\texttt{https://pdfs.semanticscholar.org/a4f4/5f3a3d7d53a40b7b2579392a5db88cc1b822.pdf}

\bibitem{PantSrinivasanMenczer} 
Pant Gautam, Srinivasan Padmini and Menczer Filippo.
\textit{Exploration versus exploitation in topic driven crawlers}.\\
\texttt{$https://www.researchgate.net/publication/2946755_Exploration_versus_Exploitation_in_Topic_Driven_Crawlers$}

\bibitem{StochasticModels} 
S. Ravi Kumar, P. Raghavan, S. Rajagopalan, D. Sivakumar, A. Tomkins, and E. Upfal.
\textit{Stochastic models for the Web graph}.\\
\texttt{http://cs.brown.edu/research/webagent/focs-2000.pdf}

\bibitem{RobotsStandard} 
Martijn Koster.
\textit{A Standard for Robot Exclusion}.\\
\texttt{http://www.robotstxt.org/orig.html}
  
\bibitem{web-crawler-selection-policy}
\texttt{http://www.cellopoint.com/media\_resources/blogs/2011/03/Web\_Crawlers}

\bibitem{distribution-of-crawling-tasks}
\texttt{http://cis.poly.edu/tr/tr-cis-2001-03.pdf}

\bibitem{serverless-characterization}
Miller, Ron (24 Nov 2015). "AWS Lambda Makes Serverless Applications A Reality". TechCrunch. Retrieved 10 July 2016.

\bibitem{diagram-icons-sources}
Sursele pictogramelor includ \texttt{https://www.iconfinder.com} si \texttt{http://simpleicon.com}.

\bibitem{aws-icons-source}
Sursa pictogramelor asociate "Amazon Web Services": \texttt{https://aws.amazon.com/architecture/icons/}

\bibitem{iterface-definition}
Definiția cuvântului \texttt{interfață} a fost adaptată pornind de la definiția de la adresa \texttt{https://www.merriam-webster.com/dictionary/interface}

\bibitem{rest-definition}
\texttt{http://www.ics.uci.edu/~fielding/pubs/dissertation/rest\_arch\_style.htm}

\bibitem{gojs-location}
Diagrama de secvență a fost generată folosind API-ul aflat la adresa \texttt{http://gojs.net/latest/samples/sequenceDiagram.html}

\bibitem{microsoft-excel}
Diagramele au fost realizate utilizând programul "Microsoft Excel" (\texttt{https://products.office.com/ro-ro/excel})

\bibitem{css-selectors}
\texttt{https://developer.mozilla.org/en-US/docs/Web/CSS/CSS\_Selectors}

\bibitem{tcp}
\texttt{https://www.ietf.org/rfc/rfc793.txt}

\bibitem{awesome-crawler}
\texttt{https://github.com/BruceDone/awesome-crawler}

\bibitem{anatomy-of-a-search-engine}
Brin, S. and Page, L. (1998) The Anatomy of a Large-Scale Hypertextual Web Search Engine, \texttt{http://ilpubs.stanford.edu:8090/361/}

\bibitem{notes-theory-distributed-systems}
Notes on Theory of Distributed Systems, CPSC 465/565: Fall 2017, James Aspnes, \texttt{http://www.cs.yale.edu/homes/aspnes/classes/465/notes.pdf}

\bibitem{web-app-hacker-handbook}
\textit{The Web Application Hacker's Handbook, 2nd Edition, Dafydd Stuttard and Marcus Pinto}

\end{thebibliography}